Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Conclusion.

>>>>

In this work we have developed a theorethical framework of computing statistical credibility
of decisions being made through a voting process.
We applied this framework to design a statistical quroum which we integrated with a web application
PeerMind.
We deployed the application in a democratic community to compare its effect in comparison with
prior time before the introduction of the web application.
Analyzing the effects of this introduction, we conclude that our hypothesis that using
crediblity as a feedback mechanism and statistical quorum as a threshold really improves
the partication of members in decision making, making it more inclusive, more engaging, and
better spend collective attention available for decision making.
